European or American? A re-examination of the transatlantic influence over the IMF

### 2025-05-27 demo/demo.qmd
Add interpretation

>>>>

## Interpretation of Results

-   $H_1$: The evidence supports the hypothesis that Europe exerts greater influence over the IMF than the United States, particularly in determining loan amounts and participation rates.

-   $H_2$: The results offer a more nuanced view.

    -   European influence is statistically significant in shaping the loan-to-GDP ratio, participation rate, and loan approval.

    -   In contrast, US influence is **only** significant in reducing the number of IMF conditions.

    -   This finding echoes @lutz2014, who argue that European actors have historically adhered more strictly to the principles of the Washington Consensus than their US counterparts.
